\chapter{FUTURE ENHANCEMENTS}

The current implementation of the video conferencing web application provides a strong foundation for real-time communication, meeting management, and user interaction. However, there are several areas where the system can be further improved to enhance performance, scalability, and user experience.

\section{AI-Based Meeting Summaries}

Future versions of the system can integrate artificial intelligence to automatically generate summaries of meetings. Using Natural Language Processing (NLP) techniques, the system can transcribe conversations and extract key points, decisions, and action items. This would greatly improve productivity and allow users to review meetings efficiently.

\section{Advanced Noise Cancellation}

Incorporating AI-driven noise suppression techniques can significantly improve audio quality. Background noise filtering using machine learning models can ensure clear communication, especially in remote or noisy environments.

\section{Mobile Application Development}

Although the current system is responsive, a dedicated mobile application for Android and iOS platforms can enhance accessibility and usability. Native mobile apps can provide better performance, push notifications, and deeper hardware integration.

\section{End-to-End Encryption}

Security can be further strengthened by implementing end-to-end encryption (E2EE). This ensures that only meeting participants can access the communication data, preventing unauthorized interception and enhancing privacy.

\section{Integration with Calendar Systems}

Integration with calendar services such as Google Calendar and Outlook can allow users to schedule and manage meetings seamlessly. Automated reminders and notifications can enhance user convenience.

\section{Recording Storage and Playback Enhancements}

Future improvements can include cloud storage for recorded meetings, along with advanced playback features such as timestamp navigation, annotations, and searchable transcripts.

\section{Real-Time Analytics Dashboard}

An analytics dashboard can be introduced to monitor meeting statistics such as participant engagement, duration, and network performance. This can provide valuable insights for improving communication efficiency.

\section{Multi-Language Support}

To make the application more inclusive, support for multiple languages can be added. This includes multilingual user interfaces and real-time translation of conversations.
